HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-14 draft/ms_v1.tex
Song: blendedness v.s. error

    In the above sections, we have pointed out the impact of high blendedness on 
    photometry through a small sample of highly blended objects.  
    Here, in Fig \ref{fig:blend}, we further explore the effect of blendedness via 
    directly plot it against the uncertainties of magnitudes and colors for both stars 
    and galaxies.

@@

    \plan{Explain why the current \cmodel{}{} algorithm has problem with measuring
          the size and shape of galaxies}

>>>>

    In the above sections, we have pointed out the impact of high blendedness on 
    photometry through a small sample of highly blended objects.  
    Here, in Fig \ref{fig:blend}, we further explore the effect of blendedness via 
    directly plotting it against the uncertainties of magnitudes and colors.

    For both PSF and \cmodel{} magnitude, we can see clear trends that high-blendeness
    ($b>0.05$ or $0.1$) objects have systematically underestimated total fluxes. 
    This effect is particularly strong for stars. 
    As for colors, higher blendedness still result in higher uncertainties for both 
    stars and galaxies, but the trends are different. 
    For stars, highly blended ones have clearly overestimated $(g-i)$ colors, and the 
    highly blended galaxies seem to have bluer $(g-i)$ colors than the true values.

    These blendedness-related uncertainties are not included in the photometric errors
    released by \hscpipe{}.  
    We therefore remind the HSC users of treating the highly blended object with 
    greater caution.

@@

    In SDSS, the structural parameters

    The CModel galaxy fitting algorithm utilizes a Bayesian prior on radius and ellipticity, largely as a way to regularize fits to low S/N and/or poorly-resolved galaxies. When combining this with the likelihood to form the posterior probability (which is then
    \plan{Explain why the current \cmodel{}{} algorithm has problem with measuring
          the size and shape of galaxies}
